---
title: "Advanced Queries"
author: "Emanuel Rodriguez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Queries}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This article outlines more advanced cases of the `cdec_query()` function.

## Query Multiple Stations 

`cdec_query()` takes just one instance of its arguments, so a user is **not** allowed 
to call 

```{r eval=FALSE}
cdec_query(station = c("ccr", "kwk"), dur_code = "h", sensor_num = "25")
```

but we can implement this same query using higher level functions.

### Using purrr

```{r, message=FALSE}
library(purrr)
library(CDECRetrieve)

stations_of_interest <- c("kwk", "ccr", "bsf")

# 'map' through the stations of interest and apply them to the function
map(stations_of_interest, function(s) {
  cdec_query(station = s, sensor_num = "25", dur_code = "h")
})
```

Using `map` will return the call to `cdec_query`, returning each as an element of a list.
This is ok, but we know that the query will return a data.frame with the same structure 
for each so we can combine these to get one dataframe. 

This can be done by using a variant of the `map` function, `map_df()`

```{r, message=FALSE}
temp_data <- map_df(stations_of_interest, function(s) {
  cdec_query(station = s, sensor_num = "25", dur_code = "h")
})

head(temp_data)
```

and now we can visualize these, 

```{r, message=FALSE, warning=FALSE}
library(ggplot2)

temp_data %>% 
  ggplot(aes(datetime, parameter_value, color=location_id)) + geom_line()
```

Great! 

We can still improve this by using some shortcut features in purrr. Namely we can 
shorten the `function` part of `map_df` using the `~` shortcut.

```{r, message=FALSE}
# here ~ tells map that this a function, and to interpret '.' as a value
# being passed from the `stations_of_interest`
map_df(stations_of_interest, ~cdec_query(., "25", "h"))
```


## Combination of multiple Arguments

The above section gave us the basic recipe for playing with multiple stations (and 
multiple of any other arguments), in this section we expand this to tackle multiple 
combinations of each. There are many ways to accomplish this, but I outline a recipe
that has worked well for me. 

First lets gather all the pieces we want to have changing,

```{r}
stations_of_interest <- c("ccr", "kwk")
sensors_of_interest <- c("25", "1")
dur_code = "h"
```

Now we can use yet another variant of `map`, `pmap_df` to pass in an 
arbitrary number of arguments, 

```{r, message=FALSE}
pmap_df(list(stations_of_interest, 
             sensors_of_interest, 
             dur_code), ~cdec_query(station = ..1, sensor_num = ..2, dur_code = ..3))
```

Here we use `..1, ..2, ..3` to refer to the first, second and third elements of the list,
we can grow this any number of arguments. 


#### Making a custom function 

In the above we don't really change `dur_code` but we still need to supply it into 
the function. We can save some time by creating a function out of `cdec_query()`, using
`purrr::partial()`, we can create a function that takes two arguments and has "dur_code"
fixed to "h". This allow us to use `map2_df` instead of `pmap_df`.

```{r, message=FALSE, warning=FALSE}
cdec_query_hourly <- purrr::partial(cdec_query, dur_code="h")

# we only have to supply two arguments
map2_df(stations_of_interest, sensors_of_interest, 
        ~cdec_query_hourly(station=.x, sensor_num=.y))
```


### All Combinations of Arguments 

Here is a way to query for a set of all combination of inputs for a given set of 
stations and sensors. 

**Note**: you need confirm these combinations make sense to query.

```{r}
stations_of_interest <- c("bsf", "kwk")
sensors_of_interest <- c("25", "27")
dur_code <- "h"

# data frame of all combinations
ins <- expand.grid(x=stations_of_interest, 
                   y=sensors_of_interest, 
                   z=dur_code, 
                   stringsAsFactors = FALSE)

pmap_df(list(ins$x, ins$y, ins$z), ~cdec_query(..1, ..2, ..3))
```







